Query Optimization for Dynamic Imputation

### 2017-03-01 paper/relatedwork.tex

\subsection{Missing Values and Statistics}

@@

In~\cite{wolf2007query}, queries over databases with missing values are
processed using a statistical approach, taking advantage of correlations between
variables. The tuples that match the original query as well as a ranking of
tuples with incomplete data that may match are returned. Our work differs in
that we allow any well-formed statistical technique to be used for imputation
and focus on returning results to the analyst as if the database had been
complete.

>>>>

\vspace{0.5in}
\subsection{Missing Values and Statistics}

@@

In~\cite{wolf2007query}, queries over databases with missing values are
processed using a statistical approach, taking advantage of correlations between
attributes. The tuples that match the original query as well as a ranking of
tuples with incomplete data that may match are returned. Our work differs in
that we allow any well-formed statistical technique to be used for imputation
and focus on returning results to the analyst as if the database had been
complete.
